Two NIRCam Arms are Better than One: How JWST Can Do More Science with NIRCam's Short-Wavelength Dispersed Hartmann Sensor

### 2016-07-03 ms.tex
I updated the figure with contours for HD 209458b retrievals both with and without the DHS.

\begin{figure*}
\centering
\includegraphics[width=1.0\textwidth]{HD209458b_solar_clear_1trans_nc_only_subset.png}
\caption{Posterior distributions an MCMC run of HD209458b without the DHS.
The H$_2$O correlates strongly with CO$_2$ and CO, meaning that improved measurements of H$_2$O with the DHS actually help improve constraints on the Carbon bearing species, even though there aren't any significant CO or CO$_2$ features in the 1-2$\mu$m range.}\label{fig:cornerRun}
\end{figure*}

>>>>

\begin{figure*}
\centering
\includegraphics[width=1.0\textwidth]{HD209458b_solar_clear_1trans_corner.png}
\caption{Posterior distributions an MCMC run of HD209458b with the DHS (blue) laid on top of that for the NIRCam girsms only without the DHS (gray).
The H$_2$O correlates strongly with CO$_2$ and CO, meaning that improved measurements of H$_2$O with the DHS actually help improve constraints on the Carbon bearing species, even though there aren't any significant CO or CO$_2$ features in the 1-2$\mu$m range.}\label{fig:cornerRun}
\end{figure*}
